\Title

### 2020-03-10 manuscript/manuscript.tex
Replace Bellow for Below on LaTeX variables

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                  \GroundSourceBellowDataConstantDepthDepthIncrement
                & \BestGroundSourceBellowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBellowDataConstantDepthScore
                  } \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                  \GroundSourceBellowDataConstantDepthDampingIncrement
                & \BestGroundSourceBellowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                  \GroundSourceBellowDataRelativeDepthDepthIncrement
                & \BestGroundSourceBellowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBellowDataRelativeDepthScore
                  } \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                  \GroundSourceBellowDataRelativeDepthDampingIncrement
                & \BestGroundSourceBellowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                  \GroundSourceBellowDataVariableDepthDepthIncrement
                & \BestGroundSourceBellowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBellowDataVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement
                & \BestGroundSourceBellowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                  \GroundSourceBellowDataVariableDepthKNearestIncrement
                & \BestGroundSourceBellowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                  \GroundSourceBellowDataVariableDepthDampingIncrement
                & \BestGroundSourceBellowDataVariableDepthDamping
                & \\
        \midrule

@@

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

>>>>

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBelowDataConstantDepthDepth
                  \GroundSourceBelowDataConstantDepthDepthIncrement
                & \BestGroundSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataConstantDepthScore
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataConstantDepthDamping
                  \GroundSourceBelowDataConstantDepthDampingIncrement
                & \BestGroundSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBelowDataRelativeDepthDepth
                  \GroundSourceBelowDataRelativeDepthDepthIncrement
                & \BestGroundSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataRelativeDepthScore
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataRelativeDepthDamping
                  \GroundSourceBelowDataRelativeDepthDampingIncrement
                & \BestGroundSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBelowDataVariableDepthDepth
                  \GroundSourceBelowDataVariableDepthDepthIncrement
                & \BestGroundSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBelowDataVariableDepthScore
                  } \\
            &
                & Depth factor
                & \GroundSourceBelowDataVariableDepthDepthFactor
                  \GroundSourceBelowDataVariableDepthDepthFactorIncrement
                & \BestGroundSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundSourceBelowDataVariableDepthKNearest
                  \GroundSourceBelowDataVariableDepthKNearestIncrement
                & \BestGroundSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBelowDataVariableDepthDamping
                  \GroundSourceBelowDataVariableDepthDampingIncrement
                & \BestGroundSourceBelowDataVariableDepthDamping
                & \\
        \midrule

@@

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                  \AirborneSourceBelowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                  \AirborneSourceBelowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                  \AirborneSourceBelowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                  \AirborneSourceBelowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                  \AirborneSourceBelowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBelowDataVariableDepthKNearest
                  \AirborneSourceBelowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                  \AirborneSourceBelowDataVariableDepthDampingIncrement \\
        \midrule
